Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
Slight changes to abstract and first paragraph of intro.

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch, the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a dense stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.  
The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array. 
\end{abstract}

@@

Planets with strong magnetic fields may generate radio and/or X-ray emission when interacting with energetic charged particles. 
It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}. 
Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass. 
\citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
\citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed properties of stellar wind in the proximity of the stars. They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME). 
Note that in these papers, the scaling relation of planetary magnetic fields differ from paper to paper.
In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}. 
Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.

>>>>

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch, the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a dense stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
RGHJs might be intrinsically as bright as or brighter than canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.
We examine the capabilities of low-frequency radio observatories to detect this emission and find that the signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array.
\end{abstract}

@@

Planets with strong magnetic fields may generate radio and/or X-ray emission when interacting with energetic charged particles. 
It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
Exoplanets could similarly generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons.
This process could provide an avenue to discover planets that are otherwise extremely difficult to find --- those orbiting highly-evolved stars.
Unlike traditional methods of discovering exoplanets, in which the planetary signal is a tiny perturbation on light from the star, low-frequency planetary radio emission might be an arena where planets are vastly brighter than their stars.
This paper is an exploration of the surprisingly diverse range of physical processes that lead to this emission, and the prospects for detecting radio emission from planets around giant stars with current and near-future low-frequency radio observatories.

Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}. 
Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass. 
\citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
\citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed properties of stellar wind in the proximity of the stars. They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME). 
Note that in these papers, the scaling relation of planetary magnetic fields differ from paper to paper.
In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}. 
Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
